Self Regulation Ontology Retest Data Report

### 2017-04-22 SRO_Report.Rmd
playing around with datatables

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
```

@@

##### For tasks
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman) %>%
  arrange(-spearman)
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
```

@@

##### For tasks
```{r}
datatable(cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman) %>%
  arrange(-spearman))
```
